Coherent optical association of a single molecule

### 2020-09-30 paper.tex
Clean up, regenerate PDF, update some numbers

\begin{figure*}
  \includegraphics[height=4.5cm]{fig3.pdf}
  \caption{
    (A) Fitting of Raman detuning scans at different times to a model of Raman transition
    with loss on the atom and molecule state. The combined fit is used to determine
    both the Raman Rabi frequency and the loss rates.
    (B) \todo{inset?} Two-body atom lifetime in $15 \mathrm{mW}$ of trap depth caused by
    off-resonance photoassociation.
    This is used to improve the fitting of the Raman transfer data.
    (C) Direct measurement of molecule lifetime in $15 \mathrm{mW}$ of trap depth.
    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
    The lifetime of $...$ is consistent with that measured from the Raman transition data.
    \label{f-lifetime}}
\end{figure*}

@@

Guided by coupled channel calculations, we locate the Raman resonance for the atom to molecule transition at $770... MHz$ (Fig.~\ref{f-raman}C) with a $15 mW$ tweezer at $288... GHz$ which corresponds to a $... GHz$ single photon detuning. (We can maybe add information about the prediction here?)
%% Prediction
% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288... GHz$ from our atomic state. The ground molecular state has not been observed previously in experimentally. Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state. Theory prediction was at $770... MHz$. \todo{more, mention/cite Jeremy}
The background level of $...\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state. When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is not directly detected by our imaging step.
We observed the narrowest linewidth of $.... kHz$ for the Raman resonance at a pulse time of $... ms$, which corresponds to a linewidth-pulsetime product of $...$. This is consistent with the expected value of $...$ for an ideal $\pi$ pulse which is an evidence that the transfer is coherent. In order to verify the coherence of the transfer directly, we fix the Raman frequency on resonance and scan the pulse time. Fig.~\ref{f-raman}D shows the observed Rabi oscillation between the atomic and molecular states. Fitting the data with a decaying Rabi oscillation suggests that $..\%$ of initial ground state atoms are transferred into the molecular state.

In order to understand the fidelity of molecule formation, we fit our measurements to a model that includes a Raman Rabi frequency and a finite lifetime for the final molecular state (Fig.~\ref{f-lifetime}A). We account for the effect of atomic state loss by measuring the single and two body lifetime of the atoms directly (Fig.~\ref{f-lifetime}B). The fit shows that we have a Raman Rabi frequency of $...$. The molecule we form has a lifetime of $...$ which is the main limitation on the fidelity of the transfer. The molecule lifetime can be verified directly by adding a second Raman pulse to dissociate the molecule back to atoms after a variable wait time (Fig.~\ref{f-lifetime}C). The result shows a molecular lifetime consistent with our fitting of the decaying Rabi oscillation.

>>>>

\begin{figure*}
  \includegraphics[height=4.5cm]{fig3.pdf}
  \caption{
    (A) Fitting of Raman detuning scans at different times to a model of Raman transition
    with loss on the atom and molecule state. The combined fit is used to determine
    both the Raman Rabi frequency and the loss rates.
    (B) \todo{inset?} Two-body atom lifetime in $15 \mathrm{mW}$ of trap depth caused by
    off-resonance photoassociation.
    This is used to improve the fitting of the Raman transfer data.
    (C) Direct measurement of molecule lifetime in $15 \mathrm{mW}$ of trap depth.
    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
    The lifetime is consistent with the $84.9(49) \mathrm{\mu s}$
    measured from the Raman transition data.
    \label{f-lifetime}}
\end{figure*}

@@

Guided by coupled channel calculations, we locate the Raman resonance for the atom to molecule transition at $770.59430(17) \mathrm{MHz}$ (Fig.~\ref{f-raman}C) with a $15 mW$ tweezer at $288560 GHz$ which corresponds to a $145 GHz$ single photon detuning. (We can maybe add information about the prediction here?)
%% Prediction
% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288560 GHz$ from our atomic state. The ground molecular state has not been observed previously in experimentally. Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state. Theory prediction was at $770.1 MHz$. \todo{more, mention/cite Jeremy}
The background level of $31\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state. When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is not directly detected by our imaging step.
We observed the narrowest linewidth of $8.43(81) \mathrm{kHz}$ for the Raman resonance at a pulse time of $0.1 \mathrm{ms}$, which corresponds to a linewidth-pulsetime product of $0.843(81)$. This is consistent with the expected value of $0.80$ for an ideal $\pi$ pulse which is an evidence that the transfer is coherent. In order to verify the coherence of the transfer directly, we fix the Raman frequency on resonance and scan the pulse time. Fig.~\ref{f-raman}D shows the observed Rabi oscillation between the atomic and molecular states. Fitting the data with a decaying Rabi oscillation suggests that $63\%$ of initial ground state atoms are transferred into the molecular state.

In order to understand the fidelity of molecule formation, we fit our measurements to a model that includes a Raman Rabi frequency and a finite lifetime for the final molecular state (Fig.~\ref{f-lifetime}A). We account for the effect of atomic state loss by measuring the single and two body lifetime of the atoms directly (Fig.~\ref{f-lifetime}B). The fit shows that we have a Raman Rabi frequency of $...$. The molecule we form has a lifetime of $84.9(49) \mathrm{\mu s}$ which is the main limitation on the fidelity of the transfer. The molecule lifetime can be verified directly by adding a second Raman pulse to dissociate the molecule back to atoms after a variable wait time (Fig.~\ref{f-lifetime}C). The result shows a molecular lifetime consistent with our fitting of the decaying Rabi oscillation.
